Pew Cleaning

### 2021-05-12 code/Submission.Rmd
ANOVA tests in!

---
title: "Submission"
author: "Jake Chanenson and Adriana Knight"
date: "5/7/2021"
output: pdf_document
---

@@

```{r FACE3, echo= echoval, message=FALSE}
#TODO: deal with POS fig.cap = "Key Figure 2", fig.pos = "!H"
###Data Manipulation###
## Create df of FACE3
df_f3 <- pew %>% filter(FACE3a_W49 != "No Answer" & FACE3b_W49 != "No Answer" & FACE3c_W49 != "No Answer") %>% filter(FACE3a_W49 != "Refused" & FACE3b_W49 != "Refused" & FACE3c_W49 != "Refused") %>%  dplyr::select(c(FACE3a_W49, FACE3b_W49, FACE3c_W49, groupKnow))

@@

```{r kf1-appendix-2, echo=echoval}
pew %>% drop_na(sumRTBF) %>% ggplot(aes(x = sumRTBF)) +
  geom_histogram(binwidth = 1, fill = "#a3d9b5") +
  labs (
    title = "Histogram of RTBF",
    subtitle = "How much do people think we have the right to forget?",
    x = "Number of acceptable categories to forget",
    y = "Count",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) + theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"))
```

@@

### 4. What Situations Respondent Think It Is Acceptable To Use Facial Recognition

@@

@@

@@

@@

### Bibliography

WE HAVE THE CITES I'll plot this in later - JC

>>>>

---
title: "Final Project Submission"
author: "Jake Chanenson and Adriana Knight"
date: "5/12/2021"
output: pdf_document
---

@@

```{r FACE3, echo= echoval, message=FALSE}
###Data Manipulation###
## Create df of FACE3
df_f3 <- pew %>% filter(FACE3a_W49 != "No Answer" & FACE3b_W49 != "No Answer" & FACE3c_W49 != "No Answer") %>% filter(FACE3a_W49 != "Refused" & FACE3b_W49 != "Refused" & FACE3c_W49 != "Refused") %>%  dplyr::select(c(FACE3a_W49, FACE3b_W49, FACE3c_W49, groupKnow))

@@

```{r kf1-appendix-2, echo=echoval}
pew %>% drop_na(sumRTBF) %>% ggplot(aes(x = sumRTBF)) +
  geom_histogram(binwidth = 1, fill = "#a3d9b5", color = 'black') +
  labs (
    title = "Histogram of RTBF",
    subtitle = "How much do people think we have the right to forget?",
    x = "Number of acceptable categories to forget",
    y = "Count",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) + theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"))
```

@@

### 4. What Situations Respondents Think It Is Acceptable To Use Facial Recognition

@@

By grouping the data by `PUBLICDATA_W49` results and running an ANOVA test on each group’s `sumRTBF` count variables, we are able to say with extremely high confidence (on a P-value that is extremely close to 0 with a value of `2e-16`) that there is a statistically significant difference between public and private data oriented respondents in the average number of categories of data they deem worthy of falling under the Right to Be Forgotten.

```{r KF1_Anova, echo = echoval}
rtbf_anova <- aov(sumRTBF ~ PUBLICDATA_W49, data = pew)
summary(rtbf_anova)
```

I would like to introduce one small caveat that does not delegitimize these findings, but does complicate them slightly. Due to the nature of the dummy variable `sumRTBF`, we may know how many categories, on average, respondents identify as being worthy of protection. However, we do not know *which* categories the respondents select. There are sixteen^[calculated using combinatorics: `(4 choose 0) + (4 choose 1) + (4 choose 2) + (4 choose 3) + (4 choose 4) = 16`] possible ways a respondent could answer the four Right to Be Forgotten questions. We know with certainty that participating respondents demonstrated trends in how many categories chosen, but we do *not* know with certainty if there are trends in *which* categories respondents chose.

@@

Using a 1-way ANOVA test on each of the three facets in key figure 2 -- Law Enforcement's Use Of Facial Recognition, Tech Companies' Use Of Facial Recognition, and Advertisers' Use Of Facial Recognition -- we are able to say with extremely high confidence (on a P-value that is extremely close to 0 with a value of `1.66e-14`, `5.37e-11`, and `<2e-16` respectively) that there is a statistically significant difference in the responses of those categorized as No Literacy Some Literacy High Literacy in all three facets!

```{r KF2_Anova, echo = echoval}
##Run ANOVA Tests
## Literacy level is the FACTOR
## H_{0}: No Literacy = Some Literacy = High Literacy for their trust in each group 
KF2_anova_law <- aov(as.numeric(FACE3c_W49) ~ groupKnow, data = pew)
KF2_anova_tech <- aov(as.numeric(FACE3b_W49) ~ groupKnow, data = pew)
KF2_anova_ad <- aov(as.numeric(FACE3a_W49) ~ groupKnow, data = pew)
```

*ANOVA Summary For Law Enforcement's Use Of Facial Recognition*
```{r KF2_Anova_Law, echo = echoval}
##Generate Summary
summary(KF2_anova_law)
```

*ANOVA Summary For Tech Companies' Use Of Facial Recognition*
```{r KF2_Anova_Tech, echo = echoval}
##Generate Summary
summary(KF2_anova_tech)
```

*ANOVA Summary For Advertisers' Use Of Facial Recognition*
```{r KF2_Anova_Ad, echo = echoval}
##Generate Summary
summary(KF2_anova_ad)
```

@@

Link to Datawrapper article: https://blog.datawrapper.de/divergingbars/

@@

### 2021-05-12 code/import_pew_data.Rmd
ANOVA tests in!

###groupKnow###
pew <- pew %>% mutate(groupKnow = ifelse(sumKnowFactor == 0, yes = "No Literacy",
                                   ifelse(sumKnowFactor == 1| sumKnowFactor == 2| sumKnowFactor == 3| sumKnowFactor == 4, yes = "Some Literacy", no = "High Literacy")),
               groupKnow = as_factor(groupKnow),
               .after = sumKnowFactor)
```

>>>>

###groupKnow###
pew <- pew %>% mutate(groupKnow = ifelse(sumKnowFactor == 0, yes = "No Literacy",
                                   ifelse(sumKnowFactor == 1| sumKnowFactor == 2| sumKnowFactor == 3| sumKnowFactor == 4, yes = "Some Literacy", no = "High Literacy")),
               groupKnow = as_factor(groupKnow),
               .after = sumKnowFactor)

###groupKnowNum - for ANOVA test###
pew <- pew %>% mutate(groupKnowNum = ifelse(groupKnow == "No Literacy", 1,
                                     ifelse(groupKnow == "Some Literacy", 2, 3)),
                      .after = groupKnow
                      ) 
```
